\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-08 ccs/conclude.tex
half pass
forgot

Currently, we are working on a front-end to translate Tensorflow code to \tool. The aim here is to provide a push button implementation to data scientists that generates secure implementations for their existing models.  
In the future, we would like to extend our security guarantees to malicious adversaries. However, we are currently unaware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits. The cryptographic backends continue to improve and the modular design of \tool makes it easy to integrate with new backends. We will continue integrating with the best available backends.
Finally, we will explore the possibility of mechanically verifying the implementation of our compiler.

>>>>

Currently, we are working on a front-end to translate Tensorflow code to \tool. The aim here is to provide a push button implementation  that generates secure implementations for existing Tensorflow models.  
In the future, we would like to extend our security guarantees to malicious adversaries. 
 The cryptographic backends continue to improve and the modular design of \tool makes it easy to integrate with the best available backends.
However, we are currently unaware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits.
Finally, we will explore the possibility of mechanically verifying the implementation of our compiler.
